\title{\Huge{Math 71: Algebra\\Groups of Small Order}}
\author{\Large{Amittai Siavava}}
\date{\Large{\today}}
\documentclass[11pt, reqno]{amsart}

\input{../../common/macros.tex}
\usepackage[backend=bibtex,style=science]{biblatex}
\bibliography{main.bib}
\pgfplotsset{compat=1.18}

\pagestyle{fancy}                       % fancy (allow headers, footers)
\fancyhf{}                              % clear all header/footer settings.
\cfoot{\thepage}                        % set page-numbers in footer.
% \lhead{\textit{\textbf{ Amittai, S}}}   % set name in header, left.
% \rhead{\textsc{Math 71: Algebra}}       % set class name in header, right.
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{.3pt}


\newcounter{problem}
\setcounter{problem}{0}

\renewcommand{\theenumi}{\alph{enumi}}

\begin{document}

\setlength{\headheight}{13.0pt}
\setlength{\footskip}{15.0pt}

\input{cover}
\bigskip

% INTRODUCTION
\input{01-introduction}
\input{02-setup}
\input{03-analysis}
\input{04-main-theorem}
\input{05-implications}
\input{06-conclusion}


\section{Main result}~\label{sec:thm}

We are now ready to prove Cayley's theorem, which we will prove in a slightly stronger form.

\begin{thm}[Cayley]~\label{thm:Cayleyn}
Let $G$ be a finite group of order $\#G = n$.  Then $G$ is isomorphic to a subgroup of $S_n$.
\end{thm}

We follow what we observed in the case $G=D_6$ in the previous section one step at a time.

Throughout, let $G$ be a finite group.  First, we define the permutations that come from the 
rows of the Cayley table.  Recall that in the row labelled $a$ (for $a \in G$), with $b \in G$ 
the column we have entry $ab$ (as usual suppressing $*$ and writing the group 
multiplicatively).

\begin{lem}
Let $a \in G$.  Define the map
\begin{align*}
\sigma_a \colon G &\to G \\
x &\mapsto ax
\end{align*}
Then $\sigma_a$ is a bijection, i.e., $\sigma_a \in \Sym(G)$.   
\end{lem}

\begin{proof}
We proved this in class, showing it is both injective and surjective and then that it has inverse $\sigma_{a^{-1}} \colon G \to G$ defined by $b \mapsto a^{-1}b$.
\end{proof}

We then built on this considering all of these bijections at once.

\begin{prop}~\label{prop:sigmaG}
Define the map
\begin{align*}
\sigma \colon G &\to \Sym(G) \\
a &\mapsto \sigma_a 
\end{align*}
Then $\sigma$ is an injective group homomorphism.  
\end{prop}

\begin{proof}
We first show that the map is a homomorphism.  Let $a,b \in G$.  We want to check
\[ \sigma_a \sigma_b \overset{?}{=} \sigma_{ab}. \]
These are two permutations of the set $G$.  To show that two functions are equal, we show that 
they give the same outputs.  So let $x \in G$.  Then on the left-hand side, by definition
\[ (\sigma_a \sigma_b)(x) = \sigma_a(\sigma_b(x)) = \sigma_a(bx) = a(bx) = abx. \]
This matches the right-hand side:
\[ \sigma_{ab}(x)=(ab)x = abx. \]
Thus $(\sigma_a\sigma_b)(x)=\sigma_{ab}(x)$ for all $x \in G$, so then $\sigma_a \sigma_b = 
\sigma_{ab} \in \Sym(G)$ as functions.  

To show that $\sigma$ is injective, we show that $\ker \sigma \subseteq \{1\}$.  Let $a \in G$ 
be such that $a$ maps to the identity: $\sigma_a=\id_G$.  Then for all $x \in G$ we have 
$\sigma_a(x)=\id_G(x)$, which means $ax=x$ for all $x \in G$.  If we plug in $x=1$ we get 
$a=1$, as desired.
\end{proof}

We may now conclude.

\begin{proof}[Proof of Theorem \ref{thm:Cayleyn}]
By Proposition \ref{prop:sigmaG}, we have an injective group homomorphism
$G \hookrightarrow \Sym(G)$. 
By Lemma \ref{lem:An}, we have an isomorphism $\Sym(G) \simeq S_n$, so composing 
these we get an injective group homomorphism $G \hookrightarrow S_n$.  Finally, by the 
fundamental homomorphism theorem (Corollary 
\ref{cor:injG}), we conclude that $G$ is isomorphic to its image, a subgroup of $S_n$.  
\end{proof}


\printbibliography

\end{document}
