\section*{Possible topic 2: Finite abelian groups}
Difficulty level: additional technicality (+2 bonus).
\begin{enumerate}[label=\arabic{enumi}.]
  \item Motivate the fundamental theorem of finite abelian groups (DF, section 5.2, 
  Parts 1 and 2 of Theorem 5) by analogy with a basis for a vector space, and go 
  beyond the analogy to a direct statement by considering a finite-dimensional vector
  space over the field $F=\Z/p\Z$.    
  \item Prove the fundamental theorem of finite abelian groups, using the sketch in 
  DF, section 6.1, pp.~196--197, with the following advice:
  \begin{enumalph}
  \item Give a complete proof of the recognition theorem for direct products (DF, 
  section 5.4, Theorem 9, p.~171), including a proof of DF, section 5.4, Proposition 
  8, p.~171.  
  \item Do not take DF, section 6.1, Corollary 4, for granted.  Argue directly, as 
  follows.  Let $G$ be a finite abelian group.
  \begin{itemize}
  \item For any $m \in \Z_{\geq 1}$, let $G_m \subseteq G$ be the subset of elements 
  whose order divides $m$.  Show that $G_m \leq G$ is a subgroup.  
  \item Suppose that $\#G = p^e m$ where $p \nmid m$ is prime.  Show that $G \simeq 
  G_{p^e} \times G_m$.  \emph{[Hint: to show $G_{p^e} G_m=G$, note that for any $x \
  in G$ we have $x^{p^e} \in G_m$ and $x^m \in G_{p^e}$, so then apply the extended 
  Euclidean algorithm.]}  
  \item Finally, if we have a factorization $\#G = p_1^{e_1} p_2^{e_2} \cdots 
  p_r^{e_r}$ into primes, show (by induction) that $G \simeq G_{p_1^{e_1}} \times 
  G_{p_2^{e_2}} \times \\cdots \times G_{p_r^{e_r}}$.
  \end{itemize}
  \end{enumalph}
  \item Illustrate the key steps in this somewhat involved proof by showing what 
  happens in examples.  (You can do this before, during, or after the proof.)
  \item As an application, prove that a finite subgroup $H \leq F^\times$ of the 
  multiplicative group of a field $F$ is cyclic (see DF, section 9.5, Proposition 18,
  p.~314).  We will almost surely prove DF, section 9.5, Proposition 17, p.~313, in 
  class; but you should just prove it directly (it is not necessary to know that 
  $F[x]$ is a UFD).
\end{enumerate}
